Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-30 paper.qmd
Updated the paper.qmd

algo_obj_two_curvy <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_two_curvy, 
  nldr_data = tsne_two_curvy, 
  num_x_bins = num_bins_x_two_curvy,
  col_start = "x")

@@

algo_obj_two_curvy2 <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_two_curvy, 
  nldr_data = tsne_two_curvy, 
  num_x_bins = num_bins_x_two_curvy,
  col_start = "x")

@@

algo_obj_two_curvy3 <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_two_curvy, 
  nldr_data = tsne_two_curvy, 
  num_x_bins = num_bins_x_two_curvy,
  col_start = "x")

@@

algo_obj_two_curvy3 <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_two_curvy, 
  nldr_data = umap_two_curvy, 
  num_x_bins = num_bins_x_two_curvy,
  col_start = "x")

@@

tsne_data_two_curvy2_with_hb_id <- hb_obj_tsne_two_curvy2$data_hb_id
df_all_two_curvy4 <- dplyr::bind_cols(training_data_two_curvy, tsne_data_two_curvy2_with_hb_id)
df_bin_two_curvy4 <- avg_highd_data(data = df_all_two_curvy4, col_start = "x")

@@

pacmap_data_two_curvy2_with_hb_id <- hb_obj_pacmap_two_curvy2$data_hb_id
df_all_two_curvy4 <- dplyr::bind_cols(training_data_two_curvy, pacmap_data_two_curvy2_with_hb_id)
df_bin_two_curvy4 <- avg_highd_data(data = df_all_two_curvy4, col_start = "x")

@@

gau1_model <- fit_highd_model(
  training_data = training_data_gau,
  emb_df = tsne_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  q = 0.1
)

@@

gau1_model <- fit_highd_model(
  training_data = training_data_gau,
  emb_df = umap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE
)

@@

gau1_model <- fit_highd_model(
  training_data = training_data_gau,
  emb_df = pacmap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  q = 0.1
)

@@

algo_obj_dens_clust <- gen_nldr_vis_algo_obj(
  high_d_data = one_c_shaped_data, 
  nldr_data = tsne_one_c_shaped, 
  num_x_bins = num_bins_x_one_c_shaped,
  col_start = "x")

@@

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = umap_pbmc, 
  num_x_bins = num_bins_x_pbmc,
  col_start = "x")

@@

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = umap_pbmc2, 
  num_x_bins = num_bins_x_pbmc,
  col_start = "pc")

@@

algo_obj_mnist <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_mnist, 
  nldr_data = tsne_mnist2, 
  num_x_bins = num_bins_x_mnist,
  col_start = "x")

>>>>

algo_obj_two_curvy <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_two_curvy, 
  nldr_data = tsne_two_curvy, 
  num_x_bins = num_bins_x_two_curvy)

@@

algo_obj_two_curvy2 <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_two_curvy, 
  nldr_data = tsne_two_curvy, 
  num_x_bins = num_bins_x_two_curvy)

@@

algo_obj_two_curvy3 <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_two_curvy, 
  nldr_data = tsne_two_curvy, 
  num_x_bins = num_bins_x_two_curvy)

@@

algo_obj_two_curvy3 <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_two_curvy, 
  nldr_data = umap_two_curvy, 
  num_x_bins = num_bins_x_two_curvy)

@@

tsne_data_two_curvy2_with_hb_id <- hb_obj_tsne_two_curvy2$data_hb_id
df_all_two_curvy4 <- dplyr::bind_cols(training_data_two_curvy, tsne_data_two_curvy2_with_hb_id)
df_bin_two_curvy4 <- avg_highd_data(data = df_all_two_curvy4)

@@

pacmap_data_two_curvy2_with_hb_id <- hb_obj_pacmap_two_curvy2$data_hb_id
df_all_two_curvy4 <- dplyr::bind_cols(training_data_two_curvy, pacmap_data_two_curvy2_with_hb_id)
df_bin_two_curvy4 <- avg_highd_data(data = df_all_two_curvy4)

@@

gau1_model <- fit_highd_model(
  highd_data = training_data_gau,
  nldr_data = tsne_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  q = 0.1
)

@@

gau1_model <- fit_highd_model(
  highd_data = training_data_gau,
  nldr_data = umap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  q = 0.1
)

@@

gau1_model <- fit_highd_model(
  highd_data = training_data_gau,
  nldr_data = pacmap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  q = 0.1
)

@@

algo_obj_dens_clust <- gen_nldr_vis_algo_obj(
  high_d_data = one_c_shaped_data, 
  nldr_data = tsne_one_c_shaped, 
  num_x_bins = num_bins_x_one_c_shaped)

@@

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = umap_pbmc, 
  num_x_bins = num_bins_x_pbmc)

@@

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = umap_pbmc2, 
  num_x_bins = num_bins_x_pbmc)

@@

algo_obj_mnist <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_mnist, 
  nldr_data = tsne_mnist2, 
  num_x_bins = num_bins_x_mnist)
